% {{cookiecutter.author}}
% {{cookiecutter.email}}

% === AUTHORS DECLARATION ===

\chapter*{Author's Declaration} \label{authors-declaration}
\addcontentsline{toc}{chapter}{Author's Declaration}

{% if cookiecutter.paper_type == "thesis" %}
\noindent
AUTHOR'S DECLARATION FOR ELECTRONIC SUBMISSION OF A THESIS \\ ~ \\
\noindent
I hereby declare that I am the sole author of this thesis. This is a true copy of the thesis, including any required final revisions, as accepted by my examiners.\\ ~ \\
\noindent
I authorize Ryerson University to lend this thesis to other institutions or individuals for the purpose of scholarly research. \\ ~ \\
\noindent
I further authorize Ryerson University to reproduce this thesis by photocopying or by other means, in total or in part, at the request of other institutions or individuals for the purpose of scholarly research. \\ ~ \\
\noindent
I understand that my thesis may be made electronically available to the public.

{% elif cookiecutter.paper_type == "major research paper" %}
\noindent
AUTHOR'S DECLARATION FOR ELECTRONIC SUBMISSION OF A MRP \\ ~ \\
\noindent
I hereby declare that I am the sole author of this MRP. This is a true copy of the MRP, including any required final revisions. \\ ~ \\
\noindent
I authorize Ryerson University to lend this MRP to other institutions or individuals for thepurpose of scholarly research. \\ ~ \\
\noindent
I further authorize Ryerson University to reproduce this MRP by photocopying or by other means, in total or in part, at the request of other institutions or individuals for the purpose of scholarly research. \\ ~ \\
\noindent
I understand that my MRP may be made electronically available to the public.

{% elif cookiecutter.paper_type == "dissertation" %}
\noindent
AUTHOR'S DECLARATION FOR ELECTRONIC SUBMISSION OF A DISSERTATION \\ ~ \\
\noindent
I hereby declare that I am the sole author of this dissertation. This is a true copy of the dissertation, including any required final revisions, as accepted by my examiners. \\ ~ \\
\noindent
I authorize Ryerson University to lend this dissertation to other institutions or individuals for the purpose of scholarly research. \\ ~ \\
\noindent
I further authorize Ryerson University to reproduce this dissertation by photocopying or by other means, in total or in part, at the request of other institutions or individuals for the purpose of scholarly research. \\ ~ \\
\noindent
I understand that my dissertation may be made electronically available to the public.

{% endif -%}